Determining Bravais Lattice Types

### 2025-11-23 SELLA/Sella_OLD.tex
just saving work

@@

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage{bm}
\usepackage[fleqn]{amsmath}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `basename #1 .tif`.png}
%\usepackage{amsbsy}
\usepackage{float}
\usepackage{url}
%\usepackage{yfonts}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[outdir=./]{epstopdf}
\usepackage{epsfig}
\usepackage{booktabs}

@@

@@

	\begin{table}
		\caption{The 21 non-triclinic Delone types with the count of representations.
			The asterisks indicate non-crystallographic types.}
		\label{table:TypeCounts}
		\begin{tabular}{lr}
			Delone type & Count    \\
			\midrule
			H4&12\\
			C1&1\\
			C3&3\\
			C5&16\\
			H1&4\\
			H3&12\\
			T1&3\\
			T2&6\\
			T5&48\\
			O1A&3\\
			O1B&1\\
			O2&6\\
			O3*&9\\
			O4&36\\
			O5&16\\
			M1A&6\\
			M1B&3\\
			M2A&12\\
			M2B*&12\\
			M3*&18\\
			M4&12\\
			\bottomrule
		\end{tabular}
	\end{table}

	\fontseries{Courier}{
		\begin{table}
			\caption{Projectors for the 24 Delone types}
			\label{table:DeloneTypes}
			\begin{tabular}{lcl}
				\toprule
				C1  & (cI) & [1 1 1 1 1 1/  1 1 1 1 1 1/  1 1 1 1 1 1/  1 1 1 1 1 1/  1 1 1 1 1 1/  1 1 1 1 1 1] \\ 
				C3  & (cF) & [1 1 0 1 1 0/  1 1 0 1 1 0/  0 0 0 0 0 0/  1 1 0 1 1 0/  1 1 0 1 1 0/  0 0 0 0 0 0] \\ 
				C5  & (cP) & [0 0 0 0 0 0/  0 0 0 0 0 0/  0 0 0 0 0 0/  0 0 0 1 1 1/  0 0 0 1 1 1/  0 0 0 1 1 1] \\ \\

				T1  & (tI) & [1 1 0 1 1 0/  1 1 0 1 1 0/  0 0 1 0 0 1/  1 1 0 1 1 0/  1 1 0 1 1 0/  0 0 1 0 0 1] \\ 
				T2  & (tI) & [1 1 0 1 1 0/  1 1 0 1 1 0/  0 0 0 0 0 0/  1 1 0 1 1 0/  1 1 0 1 1 0/  0 0 0 0 0 1] \\ 
				T5  & (tP) & [0 0 0 0 0 0/  0 0 0 0 0 0/  0 0 0 0 0 0/  0 0 0 1 1 0/  0 0 0 1 1 0/  0 0 0 0 0 1] \\ \\

				H1  & (hR) & [1 1 1 0 0 0/  1 1 1 0 0 0/  1 1 1 0 0 0/  0 0 0 1 1 1/  0 0 0 1 1 1/  0 0 0 1 1 1] \\ 
				H3  & (hR) & [1 1 0 0 1 0/  1 1 0 0 1 0/  0 0 0 0 0 0/  0 0 0 1 0 0/  1 1 0 0 1 0/  0 0 0 0 0 0] \\
				H4  & (hP) & [0 0 0 0 0 0/  0 0 0 0 0 0/  0 0 1 1 1 0/  0 0 1 1 1 0/  0 0 1 1 1 0/  0 0 0 0 0 1] \\ \\

				O1A & (oF) & [1 1 0 1 1 0/  1 1 0 1 1 0/  0 0 1 0 0 0/  1 1 0 1 1 0/  1 1 0 1 1 0/  0 0 0 0 0 1] \\ 
				O1B & (oI) & [1 0 0 1 0 0/  0 1 0 0 1 0/  0 0 1 0 0 1/  1 0 0 1 0 0/  0 1 0 0 1 0/  0 0 1 0 0 1] \\ 
				O2  & (oI) & [1 0 0 0 1 0/  0 1 0 1 0 0/  0 0 0 0 0 0/  0 1 0 1 0 0/  1 0 0 0 1 0/  0 0 0 0 0 1] \\ 
				O3  & (oI) & [1 0 0 1 0 0/  0 1 0 0 1 0/  0 0 0 0 0 0/  1 0 0 1 0 0/  0 1 0 0 1 0/  0 0 0 0 0 0] \\ 
				O4  & (oS) & [0 0 0 0 0 0/  0 0 0 0 0 0/  0 0 1 0 0 0/  0 0 0 1 1 0/  0 0 0 1 1 0/  0 0 0 0 0 1] \\ 
				O5  & (oP) & [0 0 0 0 0 0/  0 0 0 0 0 0/  0 0 0 0 0 0/  0 0 0 1 0 0/  0 0 0 0 1 0/  0 0 0 0 0 1] \\ \\

				M1A & (mC) & [1 1 0 0 0 0/  1 1 0 0 0 0/  0 0 1 0 0 0/  0 0 0 1 1 0/  0 0 0 1 1 0/  0 0 0 0 0 1] \\ 
				M1B & (mC) & [1 0 0 1 0 0/  0 1 0 0 1 0/  0 0 1 0 0 0/  1 0 0 1 0 0/  0 1 0 0 1 0/  0 0 0 0 0 1] \\ 
				M2A & (mC) & [1 0 0 1 0 0/  0 1 0 0 1 0/  0 0 0 0 0 0/  1 0 0 1 0 0/  0 1 0 0 1 0/  0 0 0 0 0 1] \\ 
				M2B & (mC) & [1 0 0 0 0 0/  0 1 0 1 0 0/  0 0 0 0 0 0/  0 1 0 1 0 0/  0 0 0 0 1 0/  0 0 0 0 0 1] \\ 
				M3  & (mC) & [1 0 0 0 0 0/  0 1 0 0 1 0/  0 0 0 0 0 0/  0 0 0 1 0 0/  0 1 0 0 1 0/  0 0 0 0 0 0] \\ 
				M4  & (mP) & [0 0 0 0 0 0/  0 0 0 0 0 0/  0 0 1 0 0 0/  0 0 0 1 0 0/  0 0 0 0 1 0/  0 0 0 0 0 1] \\ \\

				A1  & (aP) & [1 0 0 0 0 0/  0 1 0 0 0 0/  0 0 1 0 0 0/  0 0 0 1 0 0/  0 0 0 0 1 0/  0 0 0 0 0 1] \\ 
				A2  & (aP) & [1 0 0 0 0 0/  0 1 0 0 0 0/  0 0 0 0 0 0/  0 0 0 1 0 0/  0 0 0 0 1 0/  0 0 0 0 0 1] \\ 
				A3  & (aP) & [1 0 0 0 0 0/  0 1 0 0 0 0/  0 0 0 0 0 0/  0 0 0 1 0 0/  0 0 0 0 1 0/  0 0 0 0 0 0] \\ \\				
				\bottomrule
			\end{tabular}
		\end{table}
	}
	% Postscript figures can be included with multiple figure blocks

@@

>>>>

%Table 3. Illustration of the power of the 'matrix approach to symmetry'
%The initial cell was originally tested by Himes & Mighell (1987a). BLAF confirmed the reported cubic F-centred cell with a = 15.728 A
%and, in addition, calculated the estimated error in the cell edge and produced the admitted subgroup sequence. The
%output for cells 2-5 has been shortened and rearranged. The execution time on the PDI 1/44 computer was 9.8 s.
%INITIAL UNIT CELL DATA
%. . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . .
%. . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . .
%Real parameters and errors
%a = 19.2600(9) alpha = 5.7696(134)
%b = 63.8825(62) beta = 19.4709(129)
%c = 27.2394(27) gamma = 17.2952(126)
%
%SEL_2025-09-18.11_13_13_2314_0.svg
%SEL_2025-09-18.11_13_13_2314_0_fit_plots.svg
%

@@

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage{bm}
\usepackage[fleqn]{amsmath}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `basename #1 .tif`.png}
%\usepackage{amsbsy}
\usepackage{float}
\usepackage{url}
%\usepackage{yfonts}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[outdir=./]{epstopdf}
\usepackage{epsfig}
\usepackage{booktabs}
\usepackage{makecell}

@@

\begin{table}[htbp]
	\centering
	\renewcommand{\arraystretch}{1.3}
	\begin{tabular}{@{}p{4cm} p{5.5cm} p{5.5cm}@{}}
		\toprule
		\textbf{Property} & \textbf{Phase II (Room Temp)} & \textbf{Phase I (Low Temp)} \\
		\midrule
		Crystal System & Triclinic & Monoclinic \\
		Space Group & \textit{P$\bar{1}$} & \textit{C2/c} or \textit{Cc} \\
		Z (Formula Units) & 2 & 8 \\
		Unit Cell Parameters &
		\makecell[l]{
			$a = 7.485$ Å \\
			$b = 7.515$ Å \\
			$c = 7.520$ Å \\
			$\alpha = 89.98^\circ$ \\
			$\beta = 90.01^\circ$ \\
			$\gamma = 90.03^\circ$ \\
			$V \approx 423$ Å$^3$
		} &
		\makecell[l]{
			$a = 10.60$ Å \\
			$b = 18.30$ Å \\
			$c = 7.52$ Å \\
			$\beta = 92.8^\circ$ \\
			$V \approx 1457$ Å$^3$
		} \\
		Metric Symmetry & Nearly Cubic (pseudo-symmetry) & Monoclinic \\
		Transformation Proposed &
		\makecell[l]{
			Non-unimodular matrix: \\
			$\begin{bmatrix}
				2 & 1 & 0 \\
				0 & 1 & 0 \\
				0 & 0 & 1
			\end{bmatrix}$ \\
			Yields monoclinic cell: \\
			$a \approx 15.73$ Å, $b \approx 9.07$ Å, \\
			$c \approx 6.44$ Å, $\beta \approx 92.8^\circ$
		} & — \\
		Key Insight &
		\makecell[l]{
			Pseudo-symmetry masks true triclinic \\
			structure; reinterpretation improves \\
			crystallographic clarity
		} &
		\makecell[l]{
			Cation disorder and complex packing \\
			in monoclinic symmetry
		} \\
		\bottomrule
	\end{tabular}
	\caption{Summary of structural phases for [(CH$_3$)$_4$N]CuCl$_3$ from Marsh (1988).}
\end{table}

@@

	\begin{table}
		\caption{The 21 non-triclinic Delone types with the count of permutations.
			The asterisks indicate non-crystallographic types.}
		\label{table:TypeCounts}
		\begin{tabular}{lr}
			Delone type & Count    \\
			\midrule
			H4&12\\
			C1&1\\
			C3&3\\
			C5&16\\
			H1&4\\
			H3&12\\
			T1&3\\
			T2&6\\
			T5&48\\
			O1A&3\\
			O1B&1\\
			O2&6\\
			O3*&9\\
			O4&36\\
			O5&16\\
			M1A&6\\
			M1B&3\\
			M2A&12\\
			M2B*&12\\
			M3*&18\\
			M4&12\\
			\bottomrule
		\end{tabular}
	\end{table}

\fontseries{Courier}{
	\begin{table}
		\caption{Properly normalized projectors for the 24 Delone types}
		\label{table:DeloneTypes}
		\begin{tabular}{lclc}
			\toprule
			Type & Lattice & Projector & Characteristic \\
			\midrule
			C1  & (cI) & [1/6 1/6 1/6 1/6 1/6 1/6/ 1/6 1/6 1/6 1/6 1/6 1/6/ 1/6 1/6 1/6 1/6 1/6 1/6/ 1/6 1/6 1/6 1/6 1/6 1/6/ 1/6 1/6 1/6 1/6 1/6 1/6/ 1/6 1/6 1/6 1/6 1/6 1/6] & (rrr rrr) \\ 
			C3  & (cF) & [1/4 1/4 0 1/4 1/4 0/ 1/4 1/4 0 1/4 1/4 0/ 0 0 0 0 0 0/ 1/4 1/4 0 1/4 1/4 0/ 1/4 1/4 0 1/4 1/4 0/ 0 0 0 0 0 0] & (rr0 rr0) \\ 
			C5  & (cP) & [0 0 0 0 0 0/ 0 0 0 0 0 0/ 0 0 0 0 0 0/ 0 0 0 1/3 1/3 1/3/ 0 0 0 1/3 1/3 1/3/ 0 0 0 1/3 1/3 1/3] & (000 rrr) \\ \\

			T1  & (tI) & [1/4 1/4 0 1/4 1/4 0/ 1/4 1/4 0 1/4 1/4 0/ 0 0 1/2 0 0 1/2/ 1/4 1/4 0 1/4 1/4 0/ 1/4 1/4 0 1/4 1/4 0/ 0 0 1/2 0 0 1/2] & (rrr rrs) \\ 
			T2  & (tI) & [1/4 1/4 0 1/4 1/4 0/ 1/4 1/4 0 1/4 1/4 0/ 0 0 0 0 0 0/ 1/4 1/4 0 1/4 1/4 0/ 1/4 1/4 0 1/4 1/4 0/ 0 0 0 0 0 1] & (rr0 rrs) \\ 
			T5  & (tP) & [0 0 0 0 0 0/ 0 0 0 0 0 0/ 0 0 0 0 0 0/ 0 0 0 1/2 1/2 0/ 0 0 0 1/2 1/2 0/ 0 0 0 0 0 1] & (000 rrs) \\ \\

			H1  & (hR) & [1/3 1/3 1/3 0 0 0/ 1/3 1/3 1/3 0 0 0/ 1/3 1/3 1/3 0 0 0/ 0 0 0 1/3 1/3 1/3/ 0 0 0 1/3 1/3 1/3/ 0 0 0 1/3 1/3 1/3] & (rrr sss) \\ 
			H3  & (hR) & [1/4 1/4 0 0 1/4 0/ 1/4 1/4 0 0 1/4 0/ 0 0 0 0 0 0/ 0 0 0 1 0 0/ 1/4 1/4 0 0 1/4 0/ 0 0 0 0 0 0] & (rr0 sr0) \\
			H4  & (hP) & [0 0 0 0 0 0/ 0 0 0 0 0 0/ 0 0 1/3 1/3 1/3 0/ 0 0 1/3 1/3 1/3 0/ 0 0 1/3 1/3 1/3 0/ 0 0 0 0 0 1] & (00r rrs) \\ \\

			O1A & (oF) & [1/4 1/4 0 1/4 1/4 0/ 1/4 1/4 0 1/4 1/4 0/ 0 0 1 0 0 0/ 1/4 1/4 0 1/4 1/4 0/ 1/4 1/4 0 1/4 1/4 0/ 0 0 0 0 0 1] & (rrs rrt) \\ 
			O1B & (oI) & [1/2 0 0 1/2 0 0/ 0 1/2 0 0 1/2 0/ 0 0 1/2 0 0 1/2/ 1/2 0 0 1/2 0 0/ 0 1/2 0 0 1/2 0/ 0 0 1/2 0 0 1/2] & (rst rst) \\ 
			O2  & (oI) & [1/2 0 0 0 1/2 0/ 0 1/2 0 1/2 0 0/ 0 0 0 0 0 0/ 0 1/2 0 1/2 0 0/ 1/2 0 0 0 1/2 0/ 0 0 0 0 0 1] & (rs0 srt) \\ 
			O3  & (oI) & [1/2 0 0 1/2 0 0/ 0 1/2 0 0 1/2 0/ 0 0 0 0 0 0/ 1/2 0 0 1/2 0 0/ 0 1/2 0 0 1/2 0/ 0 0 0 0 0 0] & (rs0 rs0) \\ 
			O4  & (oS) & [0 0 0 0 0 0/ 0 0 0 0 0 0/ 0 0 1 0 0 0/ 0 0 0 1/2 1/2 0/ 0 0 0 1/2 1/2 0/ 0 0 0 0 0 1] & (00r sst) \\ 
			O5  & (oP) & [0 0 0 0 0 0/ 0 0 0 0 0 0/ 0 0 0 0 0 0/ 0 0 0 1 0 0/ 0 0 0 0 1 0/ 0 0 0 0 0 1] & (000 rst) \\ \\

			M1A & (mC) & [1/2 1/2 0 0 0 0/ 1/2 1/2 0 0 0 0/ 0 0 1 0 0 0/ 0 0 0 1/2 1/2 0/ 0 0 0 1/2 1/2 0/ 0 0 0 0 0 1] & (rrs ttu) \\ 
			M1B & (mC) & [1/2 0 0 1/2 0 0/ 0 1/2 0 0 1/2 0/ 0 0 1 0 0 0/ 1/2 0 0 1/2 0 0/ 0 1/2 0 0 1/2 0/ 0 0 0 0 0 1] & (rst rsu) \\ 
			M2A & (mC) & [1 0 0 0 0 0/ 0 1/2 0 1/2 0 0/ 0 0 0 0 0 0/ 0 1/2 0 1/2 0 0/ 0 0 0 0 1 0/ 0 0 0 0 0 1] & (rs0 stu) \\ 
			M2B & (mC) & [1/2 0 0 1/2 0 0/ 0 1/2 0 0 1/2 0/ 0 0 0 0 0 0/ 1/2 0 0 1/2 0 0/ 0 1/2 0 0 1/2 0/ 0 0 0 0 0 1] & (rs0 rst) \\ 
			M3  & (mC) & [1 0 0 0 0 0/ 0 1/2 0 0 1/2 0/ 0 0 0 0 0 0/ 0 0 0 1 0 0/ 0 1/2 0 0 1/2 0/ 0 0 0 0 0 0] & (rs0 ts0) \\ 
			M4  & (mP) & [0 0 0 0 0 0/ 0 0 0 0 0 0/ 0 0 1 0 0 0/ 0 0 0 1 0 0/ 0 0 0 0 1 0/ 0 0 0 0 0 1] & (00r stu) \\ \\

			A1  & (aP) & [1 0 0 0 0 0/ 0 1 0 0 0 0/ 0 0 1 0 0 0/ 0 0 0 1 0 0/ 0 0 0 0 1 0/ 0 0 0 0 0 1] & (rst uvw) \\ 
			A2  & (aP) & [1 0 0 0 0 0/ 0 1 0 0 0 0/ 0 0 0 0 0 0/ 0 0 0 1 0 0/ 0 0 0 0 1 0/ 0 0 0 0 0 1] & (rs0 tuv) \\ 
			A3  & (aP) & [1 0 0 0 0 0/ 0 1 0 0 0 0/ 0 0 0 0 0 0/ 0 0 0 1 0 0/ 0 0 0 0 1 0/ 0 0 0 0 0 0] & (rs0 tu0) \\ \\				
			\bottomrule
		\end{tabular}
	\end{table}
}
	% Postscript figures can be included with multiple figure blocks

@@

	\bibliography{Reduced}

	\bibliographystyle{iucr}
